% $File: report.tex
% $Date: Tue Dec 31 09:48:11 2013 +0800

\documentclass {beamer}
%\usetheme{JuanLesPins}
\usetheme{Copenhagen}
\setbeamertemplate{itemize items}[ball]
\setbeamercovered{transparent}
\setbeamertemplate{itemize subitem}[circle] % if you wnat a circle
\setbeamertemplate{blocks}[rounded][shadow=true]
%\usetheme[height=7mm]{Rochester}
\useoutertheme{infolines}
\usepackage{fontspec,amsmath,amssymb,zhspacing,verbatim}
\usepackage[backend=biber]{biblatex}


\let\Oldsum\sum
\renewcommand{\sum}{\displaystyle\Oldsum}
\let\Oldprod\prod
\renewcommand{\prod}{\displaystyle\Oldprod}

\theoremstyle{plain}

\usepackage[absolute,overlay]{textpos}
\newenvironment{reference}[2]{%
  \begin{textblock*}{\textwidth}(#1,#2)
      \footnotesize\it\bgroup\color{red!50!black}}{\egroup\end{textblock*}}

\zhspacing

\setbeamertemplate{footline} {
  \leavevmode%
  \hbox{%
    \begin{beamercolorbox}[wd=\paperwidth,ht=2.25ex]{corporatecolor}
      \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%
        \usebeamerfont{author in head/foot}
        \insertshortauthor
      \end{beamercolorbox}%
      \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,center]{title in head/foot}%
        \usebeamerfont{title in head/foot}
        \insertshorttitle
      \end{beamercolorbox}%
      \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,right]{date in head/foot}%
        \usebeamerfont{date in head/foot}\insertshortdate{}\hspace*{2em}
        \insertframenumber{} / \inserttotalframenumber\hspace*{2ex}
      \end{beamercolorbox}
    \end{beamercolorbox}
  }%
  \vskip0pt%
}

\title{Speaker Recognition}
\subtitle{SRT project of Signal Processing}
\author {Xinyu Zhou, Yuxin Wu, Tiezheng Li}
\institute{
  Department of Computer Science and Technology\\
  Tsinghua University\\
}
\date{\today}

\begin{document}

\frame[plain]{\titlepage}

\begin{frame}{Overview}
\begin{exampleblock}{\textbf{Speaker Recognition}}
  Identification of the person who is speaking by characteristics of their voice biometrics.
\end{exampleblock}
\textbf{Primary Goal}:

\begin{itemize}
    \item \textbf{Accurate} and \textbf{Efficient} \textbf{Short} utterance speaker recognition.
\end{itemize}

\textbf{Additional Goal}:
\begin{itemize}
  \item Scalability over large number of speakers.
  \item Low Latency Real-Time recognition
  \item A working Real-Time recognition system.
\end{itemize}


\end{frame}
\begin{frame}{Content}
\tableofcontents
\end{frame}

\input{VAD}
\input{features}
\section{Model}
\input{GMM}
\input{RBM}
%\input{JFA}
\begin{frame}{GUI Demo}

\end{frame}
\begin{frame}{Conclusion}
  \begin{itemize}
      \item We implemented a faster GMM, also with better performance.
      \item Accuracy is kept even under short training and testing utterance.
      \item Our system is highly accurate, can almost response in real-time.
      \item 97\% accuracy for 20$\sim$30 speakers, 95\% for 70$\sim$80 speakers.
  \end{itemize}
\end{frame}
\begin{frame}{}
  \begin{center}
  \Huge Thanks!
\end{center}
\end{frame}

\end{document}

